D.I.A.G.R.A.M.: Development of Image Analysis for Graph Recognition And Modeling

### 2025-05-05 doc/article/article.tex
Draft

% Classifier
\section{Classifier Module}
TODO
\subsection{Preprocessing}
TODO

\subsection{Model}
TODO

% Extractor
\section{Extractor Module}
The Extractor is the key component of the D.I.A.G.R.A.M. system, able to transform the raw diagram image into a structured, category-agnostic representation.
The Extractor recognizes the diagram's components, such as shapes, lines, and text, through an object detection network, and organizes them into a unified format. This representation serves as the foundation for the subsequent Transducer module, which converts the structured data into a domain-specific markup language.

\subsection{Preprocessing}
TODO
\subsection{Bounding Box Detection}
TODO
\subsection{Content Recognition}
TODO

% Transducer
\section{Transducer Module}
The Transducer is responsible for converting the unified, agnostic representation of a diagram into a domain-specific markup language. 
This transformation enables the subsequent Compiler module to generate high-quality visual outputs.

% Compiler
\section{Compiler Module}
The Compiler module is the final stage of the D.I.A.G.R.A.M. pipeline. 
Its primary role is to take the structured representation of the diagram, expressed in a markup language (e.g., Mermaid.js), and generate a high-quality, editable diagram in a visual format such as PNG.

>>>>

% Classifier
\subsection{Classifier Module}
TODO
\subsection{Extractor Module}
The Extractor is the key component of the D.I.A.G.R.A.M. system, able to transform the raw diagram image into a structured, category-agnostic representation.
The Extractor recognizes the diagram's components, such as shapes, lines, and text, through an object detection network, and organizes them into a unified format. This representation serves as the foundation for the subsequent Transducer module, which converts the structured data into a domain-specific markup language.
\subsection{Transducer Module}
The Transducer is responsible for converting the unified, agnostic representation of a diagram into a domain-specific markup language. 
This transformation enables the subsequent Compiler module to generate high-quality visual outputs.
\subsection{Compiler Module}
The Compiler module is the final stage of the D.I.A.G.R.A.M. pipeline. 
Its primary role is to take the structured representation of the diagram, expressed in a markup language (e.g., Mermaid.js), and generate a high-quality, editable diagram in a visual format such as PNG.

\section{Graph Diagram Recognition}

\subsection{Classifier Module}
\subsubsection{Preprocessing}
TODO
\subsubsection{Model}
TODO

\subsection{Extractor Module}
\subsubsection{Preprocessing}
TODO
\subsubsection{Bounding Box Detection}
TODO
\subsubsection{Content Recognition}

\subsection{Transducer Module}
\subsection{Compiler Module}
